\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-12 docs/paper.tex

\abstract{TODO}

@@

In this paper, we analyze the potential impact of this type of attack, commonly refered to as IDN Homograph Attack.
Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
Section 3 explores relevant work in the literature related to homograph attacks.
Section 4 describes the methodology of data collection and analysis adopted in this project.
Section 5 comments the different results obtained.
Section 6 addresses the ethical concerns regarding the data collection.
Section 7 presents the conclusions obtained from this project.

@@

Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language. \ref{screenshot} show the screenshots of the original url of \url{www.google.com} and its homograph.

@@

\subsection{Browsers Policy}
The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
Safari\footnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.

@@

In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
This method check each character in an url seperately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multiscript is detected by means of scripts block\footnote{\url{http://www.unicode.org/reports/tr24/}}.
His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.

>>>>

\abstract{
The invention of Unicode made it possible for non-English speaking people to enter the world of Internet. However, it also open up the possibilities of malicious use of URL. Sometimes different letters from different languages can look almost the same depending on the font. This paper mainly summarize the previous relevant work and analyze the current circumstance of Internationalized Domain Name Homograph Attack on the Internet via statistical approach on the websites from Alexa top 1 million rankings. Through the analysis results we will be able to provide some insight on this subject.
}

\keywords{Internationalized Domain Names, Homograph Attack, Phishing, Unicode, Punycode, Browser, Computer Security.}

@@

In this paper, we analyze the potential impact of this type of attack, commonly referred to as IDN Homograph Attack.
Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
Section 3 explores relevant work in the literature related to homograph attacks.
Section 4 describes the methodology of data collection and analysis adopted in this project.
Section 5 comments the different results obtained.
Section 6 addresses the ethical concerns regarding the data collection.
Section 7 presents the conclusions obtained from this project.

@@

Currently, most popular browsers will show the host name in Unicode depends on the language setting to defend IDN attack.
For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language. \ref{screenshot} show the screenshots of the original URL of \url{www.google.com} and its homograph.

@@

\subsection{Browsers Policy}
The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
Safari\footnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.

@@

In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
This method check each character in an URL separately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multi-script is detected by means of scripts block\footnote{\url{http://www.unicode.org/reports/tr24/}}.
His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.
